---
title: "lab 8"
author: "Allison Gracer"
date: "11/15/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Attach packages
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)
```

```{r}
# Read in the data
# unique(homes$city)

homes <- read_csv(here("data", "slo_homes.csv"))

```

A little bit of cleaning

Make a subset called homes_sub that only contains observations (rows) where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascedero
- Santa Maria-Orcutt

filter(City == c("San Luis Obispo"...)) this looks for these in ORDER rather than looking through it. 

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```

## Do a little exploring of our data

Summary statistics (home price, based on city and sale status):

-Find and return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status. 

```{r, include = FALSE}
homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))

# Actually I don't even want to run this code, then set eval = FALSE in code header and then it wont even try to run this code. 
# alpha indicates transparency level
#scale_x_discrete or scale_x_continuous

ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) + #if referring to a variable should be within aes
  scale_x_continuous(limits = c(0, 3e6))
```

Explore the relationship (visual data exploration) between square footage and home price. Change the point COLOR by city, and the point SHAPE by sale status.

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) +
  geom_point() +
  geom_smooth(method = lm)
```

