---
title: "lab 8"
author: "Allison Gracer"
date: "11/15/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, error = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Attach packages
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)
```

```{r}
# Read in the data
# unique(homes$city)

homes <- read_csv(here("data", "slo_homes.csv"))

```

A little bit of cleaning

Make a subset called homes_sub that only contains observations (rows) where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascedero
- Santa Maria-Orcutt

filter(City == c("San Luis Obispo"...)) this looks for these in ORDER rather than looking through it. 

```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```

## Do a little exploring of our data

Summary statistics (home price, based on city and sale status):

-Find and return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status. 

```{r, include = FALSE}
homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))

# Actually I don't even want to run this code, then set eval = FALSE in code header and then it wont even try to run this code. 
# alpha indicates transparency level
#scale_x_discrete or scale_x_continuous

ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) + #if referring to a variable should be within aes
  scale_x_continuous(limits = c(0, 3e6))
```

Explore the relationship (visual data exploration) between square footage and home price. Change the point COLOR by city, and the point SHAPE by sale status.

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) +
  geom_point() +
  geom_smooth(method = lm)
```
## Model the relationship with home price as DV (Dependent Variable)



```{r}
# Start with a saturated model (include every variable in this data set)

homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)

# Make a subset that only contains the quantitative variables

homes_quant <- homes_sub %>% 
  select(Price:PricePerSqFt) # select columns price through pricepersqft

homes_cor <- cor(homes_quant)
homes_cor

corrplot(homes_cor) #visual representation of correlations between variables

homes_lm1

# How would I explore the diagnostic plots?
plot(homes_lm1)

#run summary(homes_lm1) in console, get r squared value = 0.8457, this means that those variables can explain 84% of variance in home price (other variables we would need to capture 100% could be lot size, closeness to the ocean, etc. to get a higher value we would need additional variables that don't exist in our data set to explain 100.)

# for homes_lm2, rsquared value is 0.5268. AIC, provide quantitiave measure for different permiatations of a model that provides us some information on model fit and complexity. ideal model has high fit and is simple. worst is poor fit high complexity. AIC gives us a way to compare these things

```

Try Another model (homes_lm2) where we simplify this a bit:
-City
-Sqft
-Status

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)
homes_lm2

plot(homes_lm2)
```

Find the AIC value of each model:

```{r}
# low AIC is better fit, according to AIC homes_lm1 would be better BUT we conceptually have major issues with using LM1 so this is not all we should be thinking about. 

AIC(homes_lm1)
AIC(homes_lm2)
```

Try another permeation of this model that you think might make sense, check out and compare the model fit, outputs, and AIC value. 
```{r}
homes_lm3 <- lm(Price ~ SqFt + City + Status + Bedrooms, data = homes_sub)

summary(homes_lm3)
AIC(homes_lm3)
```


Use 'modelsummary' to show model outputs side-by-side:

```{r}
modelsummary(homes_lm1)

```

If you use modelsummary to return model outputs of multiple models, it wants you to geed it to it as a list.

```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

Which of these do i think makes sense? a model where regular sale homes have higher prices than forclosed homes, etc. 

## Start making predictions with this model

Use `broom::augment()`

```{r}
homes_predicted <- augment(homes_lm1)
```

Use the `predict()` function to try out your model on new scenarios that you create.

# MY UPDATE!!!!!